---
title: "Replication of some results from Borjas (2015)"
author: 'Alexandre Jenni and Miriam Venturini'
date: "February 2, 2019"
header-includes:
   - \usepackage{bbm}
   - \usepackage{subfig}
   - \usepackage{dcolumn}
   - \usepackage{amsthm}
   - \usepackage{amsmath}
   - \usepackage{float}
   - \usepackage{graphicx}
output: pdf_document
bibliography: references.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

For this assignment, we replicate (roughly) some figures and difference-in-difference estimates from _The wage impact of the Marielitos: a reappraisal_ [@borjas15].
In this paper, Borjas investigates the effects of a large and unexpected labor supply shock generated by Cuban immigrants (known as the Marielitos) on Miami's labor market.
In contrast to Card's original study [-@card90], Borjas estimates that the influx of immigrants has a seizable impact on wages and employment of local workers.
Borjas explains the absence of effects in Card's study by the use of the wrong treatment group[^1].
Indeed, Card looks at the labor outcomes of all prime-aged men workers, while the Cuban immigrants are arguably more likely to be close substitutes for low-skilled workers (high-school dropouts) only.



[^1]: Borjas also has issues with the method used by Card to select the control group.

We attempt to replicate the following figures and estimates from Borjas' paper:
 1. Figure 2
 2. The Card placebo and Miami series in Figure 3A
 3. Columns "Card placebo" and "All cities" of Table 5A of the working paper.


In addition to those results, which are computed using the subsample of high-school dropouts, we also provide analogous results for high-school graduates. We do not replicate exactly the original coefficients because we use a different reference year for the Consumer Price Index (CPI) and are not able to reproduce exactly some of the sample restrictions of the original study. Nevertheless, the results are quantitatively very similar.


# Summary Plots
In his study, Card constructs a control group using four cities that are similar in observed characteristics to Miami: Atlanta, Los Angeles, Houston, and Tampa.
Borjas refers to these four cities as "Card" control group.

## 1. Trend in the wage of low-skill workers 1976-1992.
We first attempt to replicate Figure 2 and Figure 3a of Borjas (2015).
These are shown in Figure 1 and Figure 2 of this report, which are automatically updated if they change.

```{r fig-nohs, fig.align="center", fig.pos="H", echo = FALSE, fig.cap = 'Log weekly wage of high school dropouts, Miami vs. all other US cities', fig.subcap = c('Subcaption1', 'Subcaption2'), fig.show = "hold", out.width = '.70\\linewidth', fig.asp = 1, fig.ncol = 1}
knitr::include_graphics( c("../../out/figures/trend_log_wage_no_hs_miami_vs_not_miami.pdf"))
```

```{r fig-nohsc, fig.align="center", fig.pos="H", echo = FALSE, fig.cap = 'Log weekly wage of high school dropouts, Miami vs. Card placebo', fig.subcap = c('Subcaption1', 'Subcaption2'), fig.show = "hold", out.width = '.70\\linewidth', fig.asp = 1, fig.ncol = 1}
knitr::include_graphics( c("../../out/figures/trend_log_wage_no_hs_miami_vs_card.pdf"))
```

## 2. Trend in the wage of skilled workers 1976-1992.
Taking advantage of Snakemake, we can produce analogous graphs for the subsample
of high-school graduates with a few additional lines of codes.

```{r fig-fighs, fig.align="center", fig.pos="H", echo = FALSE, fig.cap = 'Log weekly wage of high school graduates, Miami vs. all other US cities', fig.subcap = c('Subcaption1', 'Subcaption2'), fig.show = "hold", out.width = '.70\\linewidth', fig.asp = 1, fig.ncol = 1}
knitr::include_graphics( c("../../out/figures/trend_log_wage_hs_more_miami_vs_not_miami.pdf"))
```

```{r fig-fighsc, fig.align="center", fig.pos="H", echo = FALSE, fig.cap = 'Log weekly wage of high school graduates, Miami vs. Card placebo', fig.subcap = c('Subcaption1', 'Subcaption2'), fig.show = "hold", out.width = '.70\\linewidth', fig.asp = 1, fig.ncol = 1}
knitr::include_graphics( c("../../out/figures/trend_log_wage_hs_more_miami_vs_card.pdf"))
```


# Regression Tables

There are 2 tables in our paper. Table 1 attempts to replicate columns "Card placebo" and "All cities" of Table 5A of Borjas' working paper.
\input{../../out/tables/table_did_no_hs.tex}

In Table 2, we produce analogous results for the subsample of high-school graduates.
\input{../../out/tables/table_did_hs_more.tex}

# Conclusion

Thanks for reading!

# References
